Unit tests

### 2018-03-08 Tests.Rmd
put the mtime function in its own file
minor tweaks to testing

@@

<!--Set up some test data-->
```{r test_copula_function_flexible_data, echo=T}
#Set up some test data
dl<-seq(from=0.1,by=0.1,to=0.9)
ep<-c(.05,-.03,.02,-.1,-.09,.05,.1,-.08,.05)
vi<-dl+ep
vj<-dl-ep
```

```{r plot_vivj,echo=T}
plot_vivj<-function(vi,vj,lb,ub){
 plot(vi,vj,col="red",xlim=c(0,1),ylim=c(0,1),asp=1,cex.axis=0.5)
 axis(1, at = seq(0, 1, by = 0.1),cex.axis=0.5)
 abline(a=2*lb,b=-1,col="blue")
 abline(a=2*ub,b=-1,col="green4")
 abline(a=0,b=1)
 rect(0,0,1,1)
}
```

<!--Test the cor stat-->
```{r test_copula_function_flexible_cor, echo=T}
#Test the cor stat
source("CopulaFunctions_flexible.R")
lb=.05
ub=.45
h<-Corbds(vi,vj,lb=lb,ub=ub)
inds<-1:4
ht<-sum((vi[inds]-mean(vi))*(vj[inds]-mean(vj)))/((length(vi)-1)*sqrt(var(vi)*var(vj)))

@@

<!--Test the D2 stat-->
```{r test_copula_function_flexible_D2, echo=T}
#Test the D2 stat
source("CopulaFunctions_flexible.R")
lb=.05
ub=.45
h<-D2bds(vi,vj,lb=lb,ub=ub)
if (abs((sum(ep[1:4]^2)/2)-h)<1e-12)
{
  print("passed")
}
```

<!--Test the P stat-->
```{r test_copula_function_flexible_P, echo=T}
#Test the P stat
source("CopulaFunctions_flexible.R")
lb=0
ub=.45
vi<-c(vi[3],vi[7],vi[9])
vj<-c(vj[3],vj[7],vj[9])

# When two parallel boundary line are on the left side of vi+vj=1 line

#(vi,vj) plot in unit box : lower tail
plot_vivj(vi=vi,vj=vj,lb=lb,ub=ub)

#calling P stat for lower tail
hl<-Pbds(vi,vj,lb=lb,ub=ub)

@@

# When two parallel boundary line are on the right side of vi+vj=1 line
lb=0
ub=.4 # if ub=0.45 then hu$Au_Si = hl$Au_Si : so, it's a check on Au_Si
#(vi,vj) plot in unit box : upper tail
plot_vivj(vi=vi,vj=vj,lb=(1-ub),ub=(1-lb))

@@

# When two parallel boundary lines are on either side of vi+vj=1 line
lb=0.3
ub=0.8

@@

<!--Test the copsurrog2d stat-->
```{r test_copsurrog2d, echo=T}
#Test copsurrog2d

source("copsurrog2d.R")
set.seed(101)

#***basic tests of the function using kendall-preserving surrogates
datcop<-claytonCopula(5,2)
numpts<-1000
m<-rCopula(numpts,datcop)
plot(m[,1],m[,2],type='p')

@@

res<-copsurrog2d(m,tarcop,'kendall',3)
dim(res) 
if (sum(dim(res)==dim(m))==2)
{
  print("passed")
} else
{
  print("dim of output is wrong")
}

@@

plot(res[,1,1],res[,2,1],type='p') #should look like a Gumbel
BiCopGofTest(res[,1,1],res[,2,1],family=4) #should indicate an acceptable fit
BiCopGofTest(res[,1,2],res[,2,2],family=4) #should indicate an acceptable fit
BiCopGofTest(res[,1,3],res[,2,3],family=4) #should indicate an acceptable fit

@@

#basic tests using spearman preserving surrogates
res<-copsurrog2d(m,tarcop,'spearman',3)
dim(res)
if (sum(dim(res)==dim(m))==2)
{
  print("passed")
} else
{
  print("dim of output is wrong")
}

@@

<!--test to see whether changing the copula
markedly influences the distribution
of the spatial mean-->
```{r test_copsurrog2d_spatmean, echo=T, cache=T, cache.extra=list(mtime("copsurrog2d.R"),mtime("SkewnessAnd3CentMom.R"))}
#***test to see whether changing the copula
#markedly influences the distribution
#of the spatial mean
set.seed(101)

>>>>

<!--Basic setup-->
```{r setup, echo=F}
#Basic setup

#A function needed for caching
source("mtime.R")
```

@@

Set up some test data:
```{r test_copula_function_flexible_data, echo=T}
dl<-seq(from=0.1,by=0.1,to=0.9)
ep<-c(.05,-.03,.02,-.1,-.09,.05,.1,-.08,.05)
vi<-dl+ep
vj<-dl-ep
```

A plot function to use in testing:
```{r plot_vivj,echo=T}
plot_vivj<-function(vi,vj,lb,ub){
plot(vi,vj,col="red",xlim=c(0,1),ylim=c(0,1),asp=1,cex.axis=0.5)
axis(1, at = seq(0, 1, by = 0.1),cex.axis=0.5)
abline(a=2*lb,b=-1,col="blue")
abline(a=2*ub,b=-1,col="green4")
abline(a=0,b=1)
rect(0,0,1,1)
}
```

Test the cor statistic:
```{r test_copula_function_flexible_cor, echo=T}
source("CopulaFunctions_flexible.R")
lb=.05
ub=.45
plot_vivj(vi,vj,lb,ub)
h<-Corbds(vi,vj,lb=lb,ub=ub)
inds<-1:4
ht<-sum((vi[inds]-mean(vi))*(vj[inds]-mean(vj)))/((length(vi)-1)*sqrt(var(vi)*var(vj)))

@@

Test the D2 statistic:
```{r test_copula_function_flexible_D2, echo=T}
source("CopulaFunctions_flexible.R")
lb=.05
ub=.45
h<-D2bds(vi,vj,lb=lb,ub=ub)
if (abs((sum(ep[1:4]^2)/2)-h)<1e-12)
{
  print("passed")
}
```

Test the P statistic:
```{r test_copula_function_flexible_P, echo=T}
source("CopulaFunctions_flexible.R")

vi<-c(vi[3],vi[7],vi[9])
vj<-c(vj[3],vj[7],vj[9])

#Test for when two parallel boundary lines are on the left side of vi+vj=1 line
lb=0
ub=.45
plot_vivj(vi=vi,vj=vj,lb=lb,ub=ub)
hl<-Pbds(vi,vj,lb=lb,ub=ub)

@@

#Test for when two parallel boundary lines are on the right side of vi+vj=1 line
lb=0
ub=.4 # if ub=0.45 then hu$Au_Si = hl$Au_Si : so, it's a check on Au_Si
plot_vivj(vi=vi,vj=vj,lb=(1-ub),ub=(1-lb))

@@

#Test for when two parallel boundary lines are on opposite sides of vi+vj=1 line
lb=0.3
ub=0.8

@@

Test the copsurrog2d function:
```{r test_copsurrog2d, echo=T}
library("VineCopula")
source("copsurrog2d.R")
set.seed(101)

#***basic tests of the function using kendall-preserving surrogates
datcop<-claytonCopula(5,2)
numpts<-1000
m<-rCopula(numpts,datcop)
plot(m[,1],m[,2],type='p')
rect(0,0,1,1)

@@

res<-copsurrog2d(m,tarcop,'kendall',3)
dim(res) 
if (sum(dim(res)[1:2]==dim(m))==2)
{
  print("passed")
} else
{
  print("dim of output is wrong")
}

@@

plot(res[,1,1],res[,2,1],type='p') #should look like a Gumbel
rect(0,0,1,1)
BiCopGofTest(res[,1,1],res[,2,1],family=4) #should indicate an acceptable fit
BiCopGofTest(res[,1,2],res[,2,2],family=4) #should indicate an acceptable fit
BiCopGofTest(res[,1,3],res[,2,3],family=4) #should indicate an acceptable fit

@@

#basic tests using spearman preserving surrogates
res<-copsurrog2d(m,tarcop,'spearman',3)
dim(res)
if (sum(dim(res)[1:2]==dim(m))==2)
{
  print("passed")
} else
{
  print("dim of output is wrong")
}

@@

Test to see whether changing the copula
markedly influences the distribution
of the spatial mean:
```{r test_copsurrog2d_spatmean, echo=T, cache=T, cache.extra=list(mtime("copsurrog2d.R"),mtime("SkewnessAnd3CentMom.R"))}
set.seed(101)
